Thesis Title

### 2022-05-27 chapters/chapter_5.tex
Updates from Overleaf

>>>>

The filtered assembled sequences are mapped against the tripled reference replicons, ensuring that the assembled contigs can fully align regardless of their starting position relative to that of the provided reference sequence. This is done with minimap2 \cite{li_minimap2_2018} (version 2.22) with the following parameters: “minimap2 --cs -N 0 -t -r 10000 -g 10000 -x asm20 --eqx”.
